Transactional Memory Concurrency Verification with Landslide

### 2018-03-15 htm/paper.tex
few more verifs, some minors, spoilers!!, clarify remaining todos (down to 4!)

% syntax hilighting
\definecolor{brown}{RGB}{170,85,0}
\newcommand\flow[1]{\hilight{brown}{#1}\xspace}
\newcommand\const[1]{\hilight{brickred}{#1}\xspace}
\newcommand\call[1]{\hilight{pinkish}{#1}}

@@

MCs may instrument programs to introduce thread switches at varying granularity, which affects the number of operations $n$.
%The number of operations depends on how finely-grained the MC instruments the program to introduce thread switches.
Some target distributed systems, instrumenting only message-passing events \cite{modist};
some run multithreaded programs natively, instrumenting only the pthread API for performance \cite{dbug-ssv};
and some insert compiler instrumentation on statically-identified memory accesses \cite{chess,inspect}.
Landslide traces every memory access through the use of a simulated environment \cite{bochs},
which is important for identifying data races to use as new preemption points \cite{quicksand},
as well as for identifying when a memory conflict may cause transaction aborts.
With regard to checking for bugs,
the ``model'' the name refers to being checked may be
an external formal specification,
the program's own internal consistency checks,
or a set of expected properties encoded in the tool itself.
Landslide uses the latter two cases, checking for assertion failures
as well as deadlocks, use-after-frees, and segfaults.
For this work we also detect use of {\tt xend} outside of a transaction as a bug.

@@

\begin{table*}[t]
	\begin{center}
	\begin{tabular}{cc||r|r|r||r|r|r|r}
			&	&\multicolumn{3}{c||}{\bf Quicksand mode}&\multicolumn{4}{c}{{\bf Maximal state space mode} ({\tt -M})} \\
		\bf buggy test	& \bf params&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}& \ETA{\bf SS size (est.)} \\
		\hline
		\hline
		{\tt htm1}
			& 2,1	&\cpu{  45.78}&\wtm{9.70}&\ints{21}& \cpu{9.47}& \wtm{6.40}& \ints{21	}& \ETA{213} \\
		(assertion)
			& 2,2	&\cpu{  84.14}&\wtm{13.59}&\ints{33}& \cpu{10.39}& \wtm{7.70}& \ints{49	}& \ETA{1536} \\
			& 2,3	&\cpu{ 131.91}&\wtm{20.44}&\ints{73}& \cpu{12.83}& \wtm{9.67}& \ints{113	}& \ETA{10752} \\
			& 2,4	&\cpu{ 255.75}&\wtm{37.56}&\ints{257}& \cpu{18.63}& \wtm{15.86}& \ints{257	}& \ETA{73728} \\
		\cline{2-9}
			& 3,1	&\cpu{ 114.06}&\wtm{17.45}&\ints{15}& \cpu{9.50}& \wtm{6.79}& \ints{21	}& \ETA{13653} \\
			& 3,2	&\cpu{ 109.60}&\wtm{26.16}&\ints{49}& \cpu{10.72}& \wtm{7.97}& \ints{49	}& \ETA{393216} \\
			& 3,3	&\cpu{ 124.80}&\wtm{20.40}&\ints{73}& \cpu{13.84}& \wtm{11.01}& \ints{113	}& \ETA{11010048} \\
			& 3,4	&\cpu{ 227.49}&\wtm{35.15}&\ints{161}& \cpu{31.37}& \wtm{28.53}& \ints{257	}& \ETA{301989888} \\
		\cline{2-9}
			& 4,1	&\cpu{ 53.08}&\wtm{9.79}&\ints{15}& \cpu{9.82}& \wtm{7.00}& \ints{21	}& \ETA{873813} \\
			& 4,2	&\cpu{117.07}&\wtm{19.09}&\ints{33}& \cpu{11.54}& \wtm{8.55}& \ints{49	}& \ETA{100663296} \\
		\hline
		{\tt swapbug}
			& 2,1	&\cpu{ 70.95}&\wtm{13.45}&\ints{16}& \cpu{38.96}& \wtm{13.15}& \ints{109	}& \ETA{194} \\
		(deadlock)
			& 2,2	&\cpu{ 107.28}&\wtm{17.45}&\ints{146}& \cpu{44.73}& \wtm{19.47}& \ints{281	}& \ETA{1620} \\
			& 2,3	&\cpu{ 280.05}&\wtm{38.70}&\ints{352}& \cpu{60.30}& \wtm{35.55}& \ints{718	}& \ETA{12748} \\
			& 2,4	&\cpu{ 617.94}&\wtm{81.50}&\ints{834}& \cpu{108.58}& \wtm{82.60}& \ints{1820	}& \ETA{97823} \\
		\cline{2-9}
			& 3,1	&\cpu{1275.04}&\wtm{163.42}&\ints{771}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{184984} \\
			& 3,2	&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{3099225} \\
		\hline
		{\tt avl\_insert}
			& 2,2	&\cpu{488.07}&\wtm{64.77}&\ints{83}	&\cpu{81.00}&\wtm{40.30}&\ints{336}&\ETA{379982} \\
		(segfault+)
			% XXX: this 2,3 -M-mode bug was found *mostly* running in isolation,
			% but for the last few minutes i had another landslide running in parallel bc i thought itd time out.
			% according to variance expt, it should be rerun for a *minor* speedup, but i can't be bothered
			& 2,3	&\cpu{2670.87}&\wtm{330.45}&\ints{3066}	&\cpu{1331.79}&\wtm{1274.36}&\ints{13926}&\ETA{96248131} \\
		\cline{2-9}
			& 3,1	&\cpu{222.02}&\wtm{40.04}&\ints{28}	&\cpu{69.99}&\wtm{24.25}&\ints{78}&\ETA{1572107} \\
		% whoops, this was with the dumb lock ordering
		%	& 3,1	& 11.19	& 3.46	& 9	& 3.13	& 3.13	& 9	& 432 \\
		%	& 3,2	& 12.41	& 3.76	& 19	& 3.33	& 3.33	& 19	& 5832 \\
		%	& 3,3	& 15.77	& 4.58	& 41	& 3.95	& 3.95	& 41	& 77759 \\
		%	& 3,4	& 24.82	& 6.85	& 89	& 5.20	& 5.20	& 89	& 1026431 \\
		%\cline{2-9}
		%	& 4,1	& 702.33& 98.06	& 361	& 90.94	& 64.27	& 1607	& 138758 \\
		%	& 4,2	&9738.43&1257.20& 3023	& 674.87& 650.58& 16511	& 13755188 \\
	\end{tabular}
	\end{center}
	\caption{Landslide's bug-finding performance on various test configurations.
		Quicksand's workqueue approach optimized for fast bug-finding
		is compared against our maximum-state-space-prioritizing approach for fast verification.
		For each, we list the CPU-time and wall-clock time %(both in seconds)
		elapsed, %until the bug was found,
		plus the number of interleavings of the ultimately buggy state space tested,
		before the bug was found.
		Lastly, Landslide's state space size estimation \cite{estimation},
		though approximate at best,
		confers a sense of the exponential explosion.
	}
	\label{tab:buges}
\end{table*}

@@

\begin{itemize}
	\item {\tt htm1}: The bug from Figure~\ref{fig:htm-example}. %(assertion failure on {\tt count}).
	\item {\tt htm2}: The fixed version as in Figure~\ref{fig:htm-fixed}.
	\item {\tt counter}: Microbenchmark version of {\tt htm2} which replaces the complex failure path with a simple {\tt xadd}.
	\item {\tt swap}: Microbenchmark that swaps values in an array.
	\item {\tt swapbug}: {\tt swap} modified to introduce circular locking in the failure path. %(deadlock).
	\item {\tt avl\_insert}: AVL tree concurrent insertion test.
	\item {\tt avl\_fixed}: {\tt avl\_insert} with the AVL bug fixed. %(spoilers!!)
	\item {\tt map\_basic}: Separate-chaining hashmap concurrent insertion test.
	\item {\tt map\_basicer}: {\tt map\_basic} modified with a larger initial size to skip the resizing step.
\end{itemize}

@@

% TODO syntax hilighting
\begin{figure}[t]
	%\begin{center}
		\begin{tabular}{l}
		%\texttt{void count() \{} \\
		%\texttt{~~~~for (int i = 0; i < 1000; i++) \{} \\
		\texttt{\flow{while} (\_retry);} \\
		\texttt{\flow{if} (\call{\_xbegin}() == \const{SUCCESS}) \{} \\
		\texttt{~~~~\hilight{brickred}{tie}(\_root,inserted) = \call{\_insert}(\_root,n); } \\
		\texttt{~~~~\call{\_xend}();} \\
		\texttt{\} \flow{else} \{} \\
		\texttt{~~~~\call{pthread\_mutex\_lock}(\&\_tree\_lock);} \\
		\texttt{~~~~\_retry = \const{true};} \\
		\texttt{~~~~\hilight{brickred}{tie}(\_root,inserted) = \call{\_insert}(\_root,n); } \\
		\texttt{~~~~\_retry = \const{false};} \\
		\texttt{~~~~\call{pthread\_mutex\_unlock}(\&\_tree\_lock);} \\
		\texttt{\}} \\
		\end{tabular}
	%\end{center}
	%\caption{mario man had a very large house. or a castle.}
	\caption{Unmodified code from {\tt htmavl.cpp} with the previously-unknown bug found by Landslide.
		The transaction path fails to check {\tt \_retry},
		leading to data races and corruption just as in {\tt htm1}.
		}
	\label{fig:avlbug}
\end{figure}
	%\item Despite Quicksand's ability to optimize for finding bugs in overall smaller state spaces,
	%	this does not correlate with better CPU-time or even better wall-clock time.
	%	While possibly a consequence of the modest test size,
	%	this suggests future work should extend the Quicksand algorithm
	%	to prioritize by state space maximality as well as by state space estimate.
	%\item

@@

\newcommand\ETAdag[1]{\ETA{\ensuremath{\dagger}#1}}
\begin{table}[t]
	\begin{center}
		\begin{tabular}{cc||r|r}
			\bf test & \bf params & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\hline
			\hline
			{\tt counter}
			& 2,1 & \cpu{5.57}	& \ints{30}	\\
			& 2,2 & \cpu{15.53}	& \ints{384}	\\
			& 2,3 &\cpu{20.00}	& \ints{5280}	\\
			& 2,4 &\cpu{2211.10}	& \ints{75264}	\\
			& 3,1 & \cpu{57.90}	& \ints{1960}	\\
			%& 3,2 &		& 	\\
			\hline
			{\tt htm2}
			& 2,1 & \cpu{18.57}	& \ints{294}	\\
			& 2,2 & \cpu{133.78}	& \ints{4902}	\\
			& 2,3 &\cpu{1986.98}	& \ints{79017}	\\
			& 3,1 &\cpu{11672.15}	& \ints{467730}	\\
			%& 3,2 &	&	\\
			\hline
			{\tt swap}
			& 2,1 & \cpu{38.77}	& \ints{228}	\\
			& 2,2 & &       \\ % TODO: fix, or use timeout if you HAVE to
			%[JOB 8] progress: 97913/161897 brs (60.478362%), ETA 1h 29m 30s (elapsed 59m 52s)
			% [JOB 8] TIMED OUT (60.478362%; ETA 1h 29m 30s)

			& 3,1 & \ETAdag{8d 11h} & \ETAdag{411312}	\\
			%[JOB 8] progress: 103873/411312 brs (25.254021%), ETA 8d 11h 36m 0s (elapsed 59m 42s)
			%[JOB 8] TIMED OUT (25.254021%; ETA 8d 11h 36m 0s)
			\hline
			{\tt avl\_insert}
			& 2,1 & \cpu{1083.35}	& \ints{40062}	\\
			%& 2,2 & \multicolumn{2}{c}{\em (bug!)} \\
			\hline
			{\tt avl\_fixed} % TODO
			& 2,1 & 	& 	\\
			& 2,2 & 	& 	\\
			\hline
			{\tt map\_basic}
			& 2,1 & \ETAdag{10d 16h} & \ETAdag{16388977} \\
			%[JOB 15] progress: 70330/16388977 brs (0.429130%), ETA 10d 16h 34m 15s (elapsed 43m 21s)
			%[JOB 15] TIMED OUT (0.429130%; ETA 10d 16h 34m 15s)
			\hline
			{\tt map\_basicer}
			& 2,1 & \cpu{877.44}& \ints{28635}	\\
			& 2,2 & \ETAdag{2d 6h} & \ETAdag{5925634} \\
			%[JOB 6] progress: 35042/5925634 brs (0.591363%), ETA 2d 6h 40m 30s (elapsed 21m 12s)
			%[JOB 6] TIMED OUT (0.591363%; ETA 2d 6h 40m 30s)
		\end{tabular}
	\end{center}
	\caption{Transactional tests verified (or not) by Landslide.}
	\label{tab:verifs}
\end{table}

Several larger tests we were unable to complete before the submission deadline are also shown.
%Their completion times are listed as {\em unk.}
These are indicated with $\dagger$ %\ETAdag{}
and their listed ETAs and state space sizes represent Landslide's estimate %at the moment of timeout.
after a timeout of 1 hour
(hopefully enough for data-race PPs to saturate and estimates to stablize,
although note the two estimate types use different algorithms so may disagree significantly).
%For these, Table~\ref{tab:timeouts} presents their size estimates at the moment of timeout.
Though these tests proved beyond our reach,
in contrast with the high speed expected of bug-finding results,
we believe the verification guarantee may be worth the estimated time requirement
for widely-used industrial implementations.
Future work may expand our coverage upon this frontier \cite{landslide-phdthesis}.

>>>>

% syntax hilighting
\definecolor{brown}{RGB}{170,85,0}
% \definecolor{pink}{RGB}{170,45,136} % pinkish * 4/3 % but actually looks better darker
\newcommand\flow[1]{\hilight{brown}{#1}\xspace}
\newcommand\const[1]{\hilight{brickred}{#1}\xspace}
\newcommand\call[1]{\hilight{pinkish}{#1}}

@@

MCs may instrument programs to introduce thread switches at varying granularity, which affects the number of operations $n$.
%The number of operations depends on how finely-grained the MC instruments the program to introduce thread switches.
Some target distributed systems, instrumenting only message-passing events \cite{modist};
some run multithreaded programs natively, instrumenting only the pthread API for performance \cite{dbug-ssv};
and some insert compiler instrumentation on statically-identified memory accesses \cite{chess,inspect}.
Landslide traces every memory access through the use of a simulated environment \cite{bochs},
which is important for identifying data races to use as new preemption points \cite{quicksand},
as well as for identifying when a memory conflict may cause transaction aborts.
With regard to checking for bugs,
the ``model'' the name refers to being checked may be
an external formal specification,
the program's own internal consistency checks,
or a set of expected properties encoded in the tool itself.
Landslide uses the latter two cases, checking for assertion failures
as well as deadlocks, use-after-frees, and segfaults.
For this work we also detect use of {\tt xend} outside of a transaction
or {\tt xbegin} within one as a bug.

@@

\begin{table*}[t]
	\begin{center}
	\begin{tabular}{cc||r|r|r||r|r|r|r}
			&	&\multicolumn{3}{c||}{\bf Quicksand mode}&\multicolumn{4}{c}{{\bf Maximal state space mode} ({\tt -M})} \\
		\bf buggy test	& \bf params&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}& \ETA{\bf SS size (est.)} \\
		\hline
		\hline
		{\tt htm1}
			& 2,1	&\cpu{  45.78}&\wtm{9.70}&\ints{21}& \cpu{9.47}& \wtm{6.40}& \ints{21	}& \ETA{213} \\
		(assertion)
			& 2,2	&\cpu{  84.14}&\wtm{13.59}&\ints{33}& \cpu{10.39}& \wtm{7.70}& \ints{49	}& \ETA{1536} \\
			& 2,3	&\cpu{ 131.91}&\wtm{20.44}&\ints{73}& \cpu{12.83}& \wtm{9.67}& \ints{113	}& \ETA{10752} \\
			& 2,4	&\cpu{ 255.75}&\wtm{37.56}&\ints{257}& \cpu{18.63}& \wtm{15.86}& \ints{257	}& \ETA{73728} \\
		\cline{2-9}
			& 3,1	&\cpu{ 114.06}&\wtm{17.45}&\ints{15}& \cpu{9.50}& \wtm{6.79}& \ints{21	}& \ETA{13653} \\
			& 3,2	&\cpu{ 109.60}&\wtm{26.16}&\ints{49}& \cpu{10.72}& \wtm{7.97}& \ints{49	}& \ETA{393216} \\
			& 3,3	&\cpu{ 124.80}&\wtm{20.40}&\ints{73}& \cpu{13.84}& \wtm{11.01}& \ints{113	}& \ETA{11010048} \\
			& 3,4	&\cpu{ 227.49}&\wtm{35.15}&\ints{161}& \cpu{31.37}& \wtm{28.53}& \ints{257	}& \ETA{301989888} \\
		\cline{2-9}
			& 4,1	&\cpu{ 53.08}&\wtm{9.79}&\ints{15}& \cpu{9.82}& \wtm{7.00}& \ints{21	}& \ETA{873813} \\
			& 4,2	&\cpu{117.07}&\wtm{19.09}&\ints{33}& \cpu{11.54}& \wtm{8.55}& \ints{49	}& \ETA{100663296} \\
		\hline
		{\tt swapbug}
			& 2,1	&\cpu{ 70.95}&\wtm{13.45}&\ints{16}& \cpu{38.96}& \wtm{13.15}& \ints{109	}& \ETA{194} \\
		(deadlock)
			& 2,2	&\cpu{ 107.28}&\wtm{17.45}&\ints{146}& \cpu{44.73}& \wtm{19.47}& \ints{281	}& \ETA{1620} \\
			& 2,3	&\cpu{ 280.05}&\wtm{38.70}&\ints{352}& \cpu{60.30}& \wtm{35.55}& \ints{718	}& \ETA{12748} \\
			& 2,4	&\cpu{ 617.94}&\wtm{81.50}&\ints{834}& \cpu{108.58}& \wtm{82.60}& \ints{1820	}& \ETA{97823} \\
		\cline{2-9}
			& 3,1	&\cpu{1275.04}&\wtm{163.42}&\ints{771}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{184984} \\
			& 3,2	&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{3099225} \\
		% whoops, this was with the dumb lock ordering
		%	& 3,1	& 11.19	& 3.46	& 9	& 3.13	& 3.13	& 9	& 432 \\
		%	& 3,2	& 12.41	& 3.76	& 19	& 3.33	& 3.33	& 19	& 5832 \\
		%	& 3,3	& 15.77	& 4.58	& 41	& 3.95	& 3.95	& 41	& 77759 \\
		%	& 3,4	& 24.82	& 6.85	& 89	& 5.20	& 5.20	& 89	& 1026431 \\
		%\cline{2-9}
		%	& 4,1	& 702.33& 98.06	& 361	& 90.94	& 64.27	& 1607	& 138758 \\
		%	& 4,2	&9738.43&1257.20& 3023	& 674.87& 650.58& 16511	& 13755188 \\
		\hline
		{\tt avl\_insert}
			& 2,2	&\cpu{488.07}&\wtm{64.77}&\ints{83}	&\cpu{81.00}&\wtm{40.30}&\ints{336}&\ETA{379982} \\
		(segfault+)
			% XXX: this 2,3 -M-mode bug was found *mostly* running in isolation,
			% but for the last few minutes i had another landslide running in parallel bc i thought itd time out.
			% according to variance expt, it should be rerun for a *minor* speedup, but i can't be bothered
			& 2,3	&\cpu{2670.87}&\wtm{330.45}&\ints{3066}	&\cpu{1331.79}&\wtm{1274.36}&\ints{13926}&\ETA{96248131} \\
			& 2,4	&\cpu{3259.37}&\wtm{436.50}&\ints{1639}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{???} \\
			% TODO
		\cline{2-9}
			& 3,1	&\cpu{222.02}&\wtm{40.04}&\ints{28}	&\cpu{69.99}&\wtm{24.25}&\ints{78}&\ETA{1572107} \\
			& 3,2	&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{???} \\
			% TODO
	\end{tabular}
	\end{center}
	\caption{Landslide's bug-finding performance on various test configurations.
		Quicksand's workqueue approach optimized for fast bug-finding
		is compared against our maximum-state-space-prioritizing approach for fast verification.
		For each, we list the CPU-time and wall-clock time %(both in seconds)
		elapsed, %until the bug was found,
		plus the number of interleavings of the ultimately buggy state space tested,
		before the bug was found.
		Lastly, Landslide's state space size estimation \cite{estimation},
		though approximate at best,
		confers a sense of the exponential explosion.
	}
	\label{tab:buges}
\end{table*}

@@

\begin{itemize}
	\item {\tt htm1}: The bug from Figure~\ref{fig:htm-example}. %(assertion failure on {\tt count}).
	\item {\tt htm2}: The fixed version as in Figure~\ref{fig:htm-fixed}.
	\item {\tt counter}: Microbenchmark version of {\tt htm2} which replaces the complex failure path with a simple {\tt xadd}.
	\item {\tt swap}: Microbenchmark that swaps values in an array.
	\item {\tt swapbug}: {\tt swap} modified to introduce circular locking in the failure path. %(deadlock).
	\item {\tt avl\_insert}: AVL tree concurrent insertion test.
	\item {\tt avl\_fixed}: {\tt avl\_insert} with the AVL bug fixed (spoilers!!).
	\item {\tt map\_basic}: Separate-chaining hashmap concurrent insertion test.
	\item {\tt map\_basicer}: {\tt map\_basic} modified with a larger initial size to skip the resizing step.
\end{itemize}

@@

\begin{figure}[t]
	%\begin{center}
		\begin{tabular}{l}
		%\texttt{void count() \{} \\
		%\texttt{~~~~for (int i = 0; i < 1000; i++) \{} \\
		\texttt{\flow{while} (\_retry);} \\
		\texttt{\flow{if} (\call{\_xbegin}() == \const{SUCCESS}) \{} \\
		\texttt{~~~~\hilight{brickred}{tie}(\_root,inserted) = \call{\_insert}(\_root,n); } \\
		\texttt{~~~~\call{\_xend}();} \\
		\texttt{\} \flow{else} \{} \\
		\texttt{~~~~\call{pthread\_mutex\_lock}(\&\_tree\_lock);} \\
		\texttt{~~~~\_retry = \const{true};} \\
		\texttt{~~~~\hilight{brickred}{tie}(\_root,inserted) = \call{\_insert}(\_root,n); } \\
		\texttt{~~~~\_retry = \const{false};} \\
		\texttt{~~~~\call{pthread\_mutex\_unlock}(\&\_tree\_lock);} \\
		\texttt{\}} \\
		\end{tabular}
	%\end{center}
	%\caption{mario man had a very large house. or a castle.}
	\caption{Unmodified code from {\tt htmavl.cpp} with the previously-unknown bug found by Landslide.
		The transaction path fails to check {\tt \_retry},
		leading to data races and corruption just as in {\tt htm1}.
		}
	\label{fig:avlbug}
\end{figure}
	%\item Despite Quicksand's ability to optimize for finding bugs in overall smaller state spaces,
	%	this does not correlate with better CPU-time or even better wall-clock time.
	%	While possibly a consequence of the modest test size,
	%	this suggests future work should extend the Quicksand algorithm
	%	to prioritize by state space maximality as well as by state space estimate.
	%\item

@@

\newcommand\ETAdag[1]{\ETA{\ensuremath{\dagger}#1}}
\begin{table}[h]
	\begin{center}
		\begin{tabular}{cc|r|r}
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt htm2}
			& 2,1 & \cpu{18.57}	& \ints{294}	\\
			& 2,2 & \cpu{133.78}	& \ints{4902}	\\
			& 2,3 &\cpu{1986.98}	& \ints{79017}	\\
			& 3,1 &\cpu{11672.15}	& \ints{467730}	\\
			%& 3,2 &	&	\\
			\hline
			{\tt counter}
			& 2,1 & \cpu{5.57}	& \ints{30}	\\
			& 2,2 & \cpu{15.53}	& \ints{384}	\\
			& 2,3 &\cpu{20.00}	& \ints{5280}	\\
			& 2,4 &\cpu{2211.10}	& \ints{75264}	\\
			& 3,1 & \cpu{57.90}	& \ints{1960}	\\
			%& 3,2 &		& 	\\
			\hline
			{\tt swap}
			%& 2,1 & \cpu{38.77}	& \ints{228}	\\ % pre-ignore_thr_func fix
			& 2,1 & \cpu{32.98}	& \ints{193}	\\
			& 2,2 & \cpu{3652.91}	& \ints{101150}	\\
			%[JOB 8] progress: 97913/161897 brs (60.478362%), ETA 1h 29m 30s (elapsed 59m 52s)
			% [JOB 8] TIMED OUT (60.478362%; ETA 1h 29m 30s)

			& 3,1 & \ETAdag{8d 12h} & \ETAdag{411312}	\\
			%[JOB 8] progress: 103873/411312 brs (25.254021%), ETA 8d 11h 36m 0s (elapsed 59m 42s)
			%[JOB 8] TIMED OUT (25.254021%; ETA 8d 11h 36m 0s)
			\hline
			{\tt avl\_insert}
			& 2,1 & \cpu{1083.35}	& \ints{40062}	\\
			%& 2,2 & \multicolumn{2}{c}{\em (bug!)} \\
			\hline
			{\tt avl\_fixed}
			& 2,1 & \cpu{1079.03} 	& \ints{45078} 	\\
			& 2,2 & \ETAdag{2762y}	& \ETAdag{8714863} 	\\
			%[JOB 19] progress: 45863/8714863 brs (0.526262%), ETA 2762y 28d 9h 57m 14s (elapsed 59m 25s)
			%[JOB 19] TIMED OUT (0.526262%; ETA 2762y 28d 9h 57m 14s)
			% the below is from avlfixed2,2 after running it overnight
			% eta is ever worse but i'm using the 1hr one as promised
			%[JOB 19] progress: 315672/29992026 brs (1.052520%), ETA 321008y 136d 18h 22m 12s (elapsed 6h 58m 15s)
			& 3,1 & \ETAdag{12d 2h}	& \ETAdag{11498545}	\\

			\hline
			{\tt map\_basic}
			& 2,1 & \ETAdag{10d 17h} & \ETAdag{16388977} \\
			%[JOB 15] progress: 70330/16388977 brs (0.429130%), ETA 10d 16h 34m 15s (elapsed 43m 21s)
			%[JOB 15] TIMED OUT (0.429130%; ETA 10d 16h 34m 15s)
			\hline
			{\tt map\_basicer}
			& 2,1 & \cpu{877.44}& \ints{28635}	\\
			& 2,2 & \ETAdag{2d 7h} & \ETAdag{5925634} \\
			& 3,1 & 	& 	\\ % TODO
			% ^^ running now, certified not recompiled
			%[JOB 6] progress: 35042/5925634 brs (0.591363%), ETA 2d 6h 40m 30s (elapsed 21m 12s)
			%[JOB 6] TIMED OUT (0.591363%; ETA 2d 6h 40m 30s)
		\end{tabular}
	\end{center}
	\caption{Transactional tests verified (or not) by Landslide.}
	\label{tab:verifs}
\end{table}

Several larger tests we were unable to complete before the submission deadline are also shown.
%Their completion times are listed as {\em unk.}
These are indicated with $\dagger$ %\ETAdag{}
and their listed ETAs and state space sizes represent Landslide's estimate %at the moment of timeout.
after a timeout of 1 hour
(hopefully enough for data-race PPs to saturate and estimates to stablize,
although note the two estimate types use different algorithms so may disagree significantly).
%For these, Table~\ref{tab:timeouts} presents their size estimates at the moment of timeout.
Though these tests proved beyond our reach,
in contrast with the high speed expected of bug-finding results,
%we believe
the verification guarantee may in some cases be worth the estimated time requirement
for widely-used industrial implementations.
Future work may also expand our coverage upon this frontier \cite{landslide-phdthesis}.
